# This weeks assignment we covered two subjets in data modeling (univariate, bivariate, and multivariate), and Linear Algebra. It's quite impressive the ability and power that R is capable of when 
# it comes to maths. 
# Out assignemnt for this week is the following.
________
#Find the value of inverse of a matrix, determinant of a matrix by using the following values:
#A=matrix(1:100, nrow=10)
#B=matrix(1:1000, nrow=10)

```{r}
A <- matrix(1:100, nrow=10)
B <- matrix(1:1000, nrow=10)

head(A)

head(B)

#?solve

#solve(a)

```

# we used the solve function which solves the equation a %*% x = b for x, where b can be either a vector or a matrix. Using this functin with a gave us an error code stating the following 
# " Error in solve.default(a) : Lapack routine dgesv: system is exactly singular: U[6,6] = 0" meaning it does not have an inverse. Same with B. I had toruble getting the inverse so I reflected on the reading
# and searched online for help regarding inverses of matrixs. I loaded up the MASS library and this showed the code we were looking for for matrix A & B. 

```{r}
library(MASS)
A <- matrix(1:100, nrow=10)
ginv(A)

svd(A)


ginv(B)

svd(B
    )
```

# we followed up by loading the matlib package and using the det function. This calculates the determinant of a matrix. findin

```{r}
library(MASS)
A <- matrix(1:100, nrow=10)
ginv(A)

svd(A)



```

