
#For my project I've decided to create a R package that Id be able to use for my current role as a QA Analyst. This package will sort through a file and remove unnecessary lettering and spit out a 
#workable variable that I can paste into another program for work. First we will load up the librarys we will need. 

```{r}

library(readxl)
library(tidyverse)
library(purrr)
library(stringi)
```

# I imported the data set file Ill be using to test my script and make sure its all working appropriatlly. 
```{r}

umifile <- read_excel("umifile.xlsx")
View(umifile)

umifile1 <- umifile
```
# The following is the code written to remove all the lettering and only keep the numbers from all sites

```{r}


umifile1$Sites <- stri_replace_all_regex(umifile1$Sites, pattern = c("umi-s","t","m","au","d","ch","sc"), replacement=c('','','','','','',''),
vectorize=FALSE)


```

# The final result gives us a data set without any of the lettering and only leaves the numeric values followed by dashes. This allows me a easy format to copy/paste into 
# a unix console for work to remote into sites and troubleshoot issues. 
